\section{\sc Publications}

\section{\sc VLDB 2016}\hypertarget{zhao2016vldb}{} Yiran Zhao, Shen Li, \textbf{Shaohan Hu}, Hongwei Wang, Shuochao Yao, Huajie Shao, Tarek Abdelzaher, \href{}{\emph{An Experimental Evaluation of Datacenter Workloads On Low-Power Embedded Micro Servers}}, \textsf{The 42nd International Conference on Very Large Data Bases (VLDB 2016)}, New Delhi, India, September 5--9, 2016.

\section{\sc ICDCS 2016}\hypertarget{yao2016icdcs}{} Shuochao Yao, \textbf{Shaohan Hu}, Shen Li, Yiran Zhao, Lu Su, Lance Kaplan, Aylin Yener, Tarek F. Abdelzaher, \href{}{\emph{On Source Dependency Models for Reliable Social Sensing: Algorithms and Fundamental Error Bound}}, \textsf{The 36th IEEE International Conference on Distributed Computing Systems (ICDCS 2016)}, Nara, Japan, June 27--30, 2016.

\section{\sc IPSN 2016}\hypertarget{wang2015ipsn}{} Shuochao Yao, Md Tanvir Amin, Lu Su, \textbf{Shaohan Hu}, Shen Li, Shiguang Wang, Yiran Zhao, Tarek Abdelzaher, Lance Kaplan, Charu Aggarwal, Aylin Yener, \href{}{\emph{Recursive Ground Truth Estimator for Social Data Streams}}, \textsf{The 15th ACM/IEEE International Conference on Information Processing in Sensor Networks (IPSN 2016)}, Vienna, Austria, April 11--14, 2016.

\section{\sc TMC 2016}\hypertarget{saremi2016tmc}{} Fatemeh Saremi, Omid Fatemieh, Hossein Ahmadi, Hongyan Wang, Tarek Abdelzaher, Raghu Ganti, Hengchang Liu, \textbf{Shaohan Hu}, Shen Li, Lu Su, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=7084108}{\emph{Experiences with GreenGPS -- Fuel-Efficient Navigation using Participatory Sensing}}, \textsf{IEEE Transactions on Mobile Computing (IEEE TMC)}, Vol. 15, No. 3, March 2016.

\section{\sc TMC 2015}\hypertarget{hu2015tmc}{} \textbf{Shaohan Hu}, Xiaoshan Sun, Lu Su, Tarek F. Abdelzaher, Pan Hui, Wei Zheng, Hengchang Liu, John Stankovic, \href{http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7337442}{\emph{Participatory Sensing Meets Opportunistic Sharing: Automatic Phone-to-Phone Communication in Vehicles}}, \textsf{IEEE Transactions on Mobile Computing (IEEE TMC)}, 2015.

\section{\sc RTSS 2015}\hypertarget{hu2015rtss}{} \textbf{Shaohan Hu}, Shuochao Yao, Haiming Jin, Yiran Zhao, Yitao Hu, Xiaochen Liu, Nooreddin Naghibolhosseini, Shen Li, Akash Kapoor, William Dron, Lu Su, Amotz Bar-Noy, Pedro Szekely, Ramesh Govindan, Reginald Hobbs, Tarek F. Abdelzaher, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=7383576}{\emph{Data Acquisition for Real-time Decision-making under Freshness Constraints}}, \textsf{The 36th IEEE Real-Time Systems Symposium (RTSS 2015)}, San Antonio, TX USA, December 1--4, 2015.

\section{\sc UbiComp 2015}\hypertarget{hu2015ubicomp}{} \textbf{Shaohan Hu}, Lu Su, Shen Li, Shiguang Wang, Chenji Pan, Siyu Gu, Md Tanvir Amin, Hengchang Liu, Suman Nath, Romit Roy Choudhury, Tarek F. Abdelzaher, \href{http://dl.acm.org/citation.cfm?id=2804287}{\emph{Experiences with eNav: A Low-power Vehicular Navigation System}}, \textsf{The ACM International Joint Conference on Pervasive and Ubiquitous Computing (UbiComp 2015)}, Osaka, Japan, September 7--11, 2015.

\section{\sc JRTS 2015}\hypertarget{wang2015jrts}{} Dong Wang, Tarek Abdelzaher, Lance Kaplan, Raghu Ganti, \textbf{Shaohan Hu}, Hengchang Liu, \href{http://link.springer.com/article/10.1007%2Fs11241-015-9238-8}{\emph{Reliable Social Sensing with Physical Constraints: Analytic Bounds and Performance Evaluation}}, \textsf{Journal of Real-Time Systems}, August 2015

\section{\sc ATC 2015}\hypertarget{li2015atc}{} Shen Li, \textbf{Shaohan Hu}, Raghu Ganti, Mudhakar Srivatsa, Tarek Abdelzaher, \href{https://www.usenix.org/system/files/conference/atc15/atc15-paper-li-shen.pdf}{\emph{Pyro: A Spatial-Temporal Big-Data Storage System for Dynamic Workload Hotspots}}, \textsf{USENIX Annual Technical Conference (USENIX ATC 2015)}, Santa Clara, CA USA, July 8--10, 2015.

\section{\sc TOSN 2015}\hypertarget{hu2015tosn}{} \textbf{Shaohan Hu}, Lu Su, Hengchang Liu, Hongyan Wang, Tarek F. Abdelzaher, \href{http://dl.acm.org/citation.cfm?id=2770876}{\emph{SmartRoad: Smartphone-based Crowd Sensing for Traffic Regulator Detection and Identification}}, \textsf{ACM Transactions on Sensor Networks (ACM TOSN)}, Volume 11, Issue 4, No. 55, July 2015.

\section{\sc DCOSS 2015}\hypertarget{hu2015dcoss}{} \textbf{Shaohan Hu}, Shen Li, Shuochao Yao, Lu Su, Ramesh Govindan, Reginald Hobbs, Tarek F. Abdelzaher, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=7165037}{\emph{On Exploiting Logical Dependencies for Minimizing Additive Cost Metrics in Resource-Limited Crowdsensing}}, \textsf{The 11th IEEE International Conference on Distributed Computing in Sensor Systems (DCOSS 2015)}, Fortaleza, Brazil, June 10--12, 2015.

\section{\sc IPSN 2015}\hypertarget{wang2015ipsn}{} Shiguang Wang, Lu Su, Shen Li, \textbf{Shaohan Hu}, Tanvir Amin, Hongwei Wang, Shuochao Yao, Lance Kaplan, Tarek Abdelzaher, \href{http://dl.acm.org/citation.cfm?id=2737114}{\emph{Scalable Social Sensing of Interdependent Phenomena}}, \textsf{The 14th ACM/IEEE International Conference on Information Processing in Sensor Networks (IPSN 2015)}, Seattle, WA USA, April 13--17, 2015.

\section{\sc RTAS 2015}\hypertarget{li2015rtas}{} Shen Li, \textbf{Shaohan Hu}, Tarek Abdelzaher, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=7108416}{\emph{The Packing Server for Real-time Scheduling of MapReduce Workflows}}, \textsf{The 21st IEEE Real-Time and Embedded Technology and Applications Symposium (RTAS 2015)}, Seattle, WA USA, April 13--16, 2015.

\section{\sc ICCPS 2015}\hypertarget{gao2015iccps}{} Yunlong Gao, \textbf{Shaohan Hu}, Renato Mancuso, Hongwei Wang, Minje Kim, PoLiang Wu, Lu Su, Lui Sha, Tarek Abdelzaher, \href{http://dl.acm.org/citation.cfm?id=2735960.2735965}{\emph{Exploiting Structured Human Interactions to Enhance Estimation Accuracy in Cyber-physical Systems}}, \textsf{The 6th International Conference on Cyber-Physical Systems (ICCPS 2015)}, Seattle, WA USA, April 14--16, 2015.

\section{\sc RTSS 2014}\hypertarget{su2014rtss}{} Lu Su, Qi Li, \textbf{Shaohan Hu}, Shiguang Wang, Jing Gao, Hengchang Liu, Tarek Abdelzaher, Jiawei Han, Xue Liu, Yan Gao, Lance Kaplan, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=7010369}{\emph{Generalized Decision Aggregation in Distributed Sensing Systems}}, \textsf{The 35th IEEE Real-Time Systems Symposium (RTSS 2014)}, Rome, Italy, December 2--5, 2014.

\section{\sc ICDCS 2014}\hypertarget{li2014icdcs}{} Shen Li, \textbf{Shaohan Hu}, Shiguang Wang, Lu Su, Tarek F. Abdelzaher, Indranil Gupta, Richard Pace, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6888886}{\emph{WOHA: Deadline-Aware Map-Reduce Workflow Scheduling Framework over Hadoop Cluster}}, \textsf{The 34th International Conference on Distributed Computing Systems (ICDCS 2014)}, Madrid, Spain. June 30--July 3, 2014.

\section{\sc ICAC 2014}\hypertarget{li2014icac}{} Shen Li, \textbf{Shaohan Hu}, Shiguang Wang, Siyu Gu, Chenji Pan, Tarek F. Abdelzaher, \href{https://www.usenix.org/system/files/conference/icac14/icac14-paper-li_shen.pdf}{\emph{WattValet: Heterogenous Energy Storage Management in Data Centers for Improved Power Capping}}, \textsf{The 11th International Conference on Autonomic Computing (ICAC 2014)}, Philadelphia, PA USA, June 18--20, 2014.

\section{\sc DCOSS 2014}\hypertarget{gu2014dcoss}{} Siyu Gu, Chenji Pan, Hengchang Liu, Shen Li, \textbf{Shaohan Hu}, Lu Su, Shiguang Wang, Dong Wang, Md Tanvir A Amin, Ramesh Govindan, Charu Aggarwal, Raghu Ganti, Mudhakar Srivatsa, Amotz Bar-Noy, Peter Terlecky, Tarek Abdelzaher, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6846153}{\emph{Data Extrapolation in Social Sensing for Disaster Response}}, \textsf{The 10th IEEE International Conference on Distributed Computing in Sensor Systems (DCOSS 2014)}, Marina Del Rey, CA USA, May 26--28, 2014.

\section{\sc UIUC TR 2014b}\hypertarget{wang2014uiuc}{} Dong Wang, Tarek F. Abdelzaher, Lance Kaplan, Raghu Ganti, \textbf{Shaohan Hu}, Hengchang Liu, \href{https://www.ideals.illinois.edu/handle/2142/49113}{\emph{Reliable Social Sensing with Physical Dependencies: Analytic Bounds and Performance Evaluation}}, \textsf{UIUC Technical Report}, May 15, 2014.

\section{\sc Infocom 2014}\hypertarget{hu2014infocom}{} \textbf{Shaohan Hu}, Hengchang Liu, Lu Su, Hongyan Wang, Tarek F. Abdelzaher, Pan Hui, Wei Zheng, Zhiheng Xie, John Stankovic, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6848113}{\emph{Towards Automatic Phone-to-Phone Communication for Vehicular Networking Applications}}, \textsf{The 33rd IEEE International Conference on Computer Communications (INFOCOM 2014)}, Toronto, Canada, April 27--May 2, 2014.

\section{\sc UIUC TR 2014a }\hypertarget{hu2014uiuc1}{} \textbf{Shaohan Hu}, Lu Su, Shen Li, Shiguang Wang, Chenji Pan, Siyu Gu, Md Tanvir Amin, Hengchang Liu, Suman Nath, Romit Roy Choudhury, Tarek F. Abdelzaher, \href{https://www.ideals.illinois.edu/handle/2142/48917}{\emph{eNav: Smartphone-based Energy Efficient Location Sensing for Low-Power Vehicular Navigation}}, \textsf{UIUC Technical Report}, April 25, 2014.

\section{\sc IPSN 2014}\hypertarget{hu2014ipsn}{} \textbf{Shaohan Hu}, Lu Su, Shen Li, Shiguang Wang, Chenji Pan, Siyu Gu, Md Tanvir Al Amin, Hengchang Liu, Suman Nath, Romit Roy Choudhury, Tarek F. Abdelzaher, \href{http://dl.acm.org/citation.cfm?id=2602374}{\emph{Poster Abstract: eNav -- a Smartphone-based Energy Efficient Vehicular Navigation System}}, \textsf{The 13th ACM/IEEE International Conference on Information Processing in Sensor Networks (IPSN 2014)}, Berlin, Germany, April 15--17, 2014. (\textbf{Best poster award})

\section{\sc PUC 2014}\hypertarget{lane2013puc}{} Nicholas D. Lane, Ye Xu, Hong Lu, \textbf{Shaohan Hu}, Tanzeem Choudhury, Andrew T. Campbell, Feng Zhao, \href{http://link.springer.com/article/10.1007/s00779-013-0655-1}{\emph{Community Similarity Networks}}, \textsf{ACM/Springer Journal of Personal and Ubiquitous Computing (PUC), Special Issue on Cross-Community Mining}, February, 2014.

\section{\sc RTSS 2013}\hypertarget{wang2013rtss}{} Dong Wang, Tarek F. Abdelzaher, Lance Kaplan, Raghu Ganti, \textbf{Shaohan Hu}, Hengchang Liu, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6728876}{\emph{Exploitation of Physical Constraints for Reliable Social Sensing}}, \textsf{The 34th IEEE Real-Time Systems Symposium (RTSS 2013)}, Vancouver, Canada, December 4--6, 2013.

\section{\sc SenSys 2013}\hypertarget{liu2013sensys}{} Hengchang Liu, Siyu Gu, Chenji Pan, Wei Zheng, Shen Li, \textbf{Shaohan Hu}, Shiguang Wang, Dong Wang, Tanvir Amin, Lu Su, Zhiheng Xie, Ramesh Govindan, Charu Aggarwal, Amotz Barnoy, Tarek F. Abdelzaher, \href{http://portal.acm.org/citation.cfm?id=2517431}{\emph{Demo Abstract: Extrapolation from Participatory Sensing Data}}, \textsf{The 11th ACM Conference on Embedded Networked Sensor Systems (SenSys 2013)}, Rome, Italy, November 11--15, 2013.

\section{\sc UIUC TR 2013c}\hypertarget{hu2013uiuc2}{} \textbf{Shaohan Hu}, Hengchang Liu, Lu Su, Hongyan Wang, Tarek F. Abdelzaher, \href{https://www.ideals.illinois.edu/handle/2142/45699}{\emph{SmartRoad: A Mobile Phone Based Crowd-Sourced Road Sensing System}}, \textsf{UIUC Technical Report}, August 30, 2013.

\section{\sc ICCCN 2013}\hypertarget{wang2013icccn}{} Shiguang Wang, \textbf{Shaohan Hu}, Shen Li, Hengchang Liu, Md Yusuf Sarwar Uddin, and Tarek F. Abdelzaher, \href{http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=6614152}{\emph{MINERVA: Information-Centric Programming for Social Sensing}}, \textsf{The 22nd International Conference on Computer Communications and Networks (ICCCN 2013)}, Nassau, Bahamas, July 30--August 2, 2013.

\section{\sc ICDCS 2013}\hypertarget{li2013icdcs}{} Shen Li, Shiguang Wang, Fan Yang, \textbf{Shaohan Hu}, Fatemeh Saremi, Tarek F. Abdelzaher, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6681577}{\emph{Proteus: Power Proportional Memory Cache Cluster in Data Centers}}, \textsf{The 33rd International Conference on Distributed Computing Systems (ICDCS 2013)}, Philadelphia, PA USA, July 8--11, 2013.

\section{\sc UIUC TR 2013b}\hypertarget{hu2013uiuc1}{} \textbf{Shaohan Hu}, Lu Su, Hengchang Liu, Hongyan Wang, Tarek F. Abdelzaher, \href{https://www.ideals.illinois.edu/handle/2142/43856}{\emph{SmartRoad: A Crowd-Sourced Traffic Regulator Detection and Identification System}}, \textsf{UIUC Technical Report}, April 18, 2013.

\section{\sc Infocom 2013}\hypertarget{liu2013infocom}{} Hengchang Liu, \textbf{Shaohan Hu}, Wei Zheng, Zhiheng Xie, Shiguang Wang, Pan Hui, and Tarek F. Abdelzaher, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6566935}{\emph{Efficient 3G Budget Utilization in Mobile Participatory Sensing Applications}}, \textsf{The 32nd IEEE International Conference on Computer Communications (INFOCOM 2013)}, Turin, Italy, April 14--19, 2013.

\section{\sc IPSN 2013}\hypertarget{hu2013ipsn}{} \textbf{Shaohan Hu}, Lu Su, Hengchang Liu, Hongyan Wang, Tarek F. Abdelzaher, \href{http://portal.acm.org/citation.cfm?id=2461433}{\emph{Poster Abstract: SmartRoad: A Crowd-Sourced Traffic Regulator Detection and Identification System}}, \textsf{The 12th ACM/IEEE International Conference on Information Processing in Sensor Networks (IPSN 2013)}, Philadelphia, PA USA, April 8--11, 2013.

\section{\sc UIUC TR 2013a}\hypertarget{wang2013uiuc}{} Shiguang Wang, \textbf{Shaohan Hu}, Shen Li, Hengchang Liu, Md Yusuf Sarwar Uddin, and Tarek F. Abdelzaher, \href{https://www.ideals.illinois.edu/handle/2142/42511}{\emph{MINERVA: Information-Centric Programming for Social Sensing}}, \textsf{UIUC}, January 15, 2013

\section{\sc RTSS 2012}\hypertarget{su2012rtss}{} Lu Su, \textbf{Shaohan Hu}, Shen Li, Feng Liang, Jing Gao, Tarek F. Abdelzaher, and Jiawei Han, \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6424815}{\emph{Quality of Information based Data Selection and Transmission in Wireless Sensor Networks}}, \textsf{The 33rd IEEE Real-Time Systems Symposium (RTSS 2012)}, San Juan, Puerto Rico, December 4--7, 2012.

\section{\sc UbiComp 2011}\hypertarget{lane2011ubicomp}{} Nicholas D. Lane, Ye Xu, Hong Lu, \textbf{Shaohan Hu}, Tanzeem Choudhury, Andrew T. Campbell, and Feng Zhao, \href{http://portal.acm.org/citation.cfm?id=2030160}{\emph{Enabling Large-scale Human Activity Inference on Smartphones using Community Similarity Networks (CSN)}}, \textsf{The 13th International Conference on Ubiquitous Computing (UbiComp 2011)}, Beijing, China, September 17--21, 2011. (\textbf{Best paper nominee})

\section{\sc MobiHeld 2010}\hypertarget{campbell2010mobiheld}{} Andrew T. Campbell, Tanzeem Choudhury, \textbf{Shaohan Hu}, Hong Lu, Matthew K. Mukerjee, Mashfiqui Rabbi, and Rajeev D. S. Raizada, \href{http://portal.acm.org/citation.cfm?id=1851326}{\emph{NeuroPhone: Brain-Mobile Phone Interface using a Wireless EEG Headset}}, \textsf{The 2nd ACM SIGCOMM Workshop on Networking, Systems, and Applications on Mobile Handhelds (MobiHeld 2010)}, New Delhi, India, August 30, 2010.

\section{\sc PAKDD 2010}\hypertarget{kanani2010pakdd}{} Pallika Kanani, Andrew McCallum and \textbf{Shaohan Hu}, \href{http://www.springerlink.com/content/j41w758434321108}{\emph{Resource-bounded Information Extraction: Acquiring Missing Feature Values On Demand}}, \textsf{The 14th Pacific-Asia Conference on Knowledge Discovery and Data Mining (PAKDD 2010)},Hyderabad, India. June 21--24, 2010. (\textbf{Best student paper runner-up award})
